Impact of Context in the Perception of a Robot

### 2015-07-02 main.tex
Minor fix to one subtitle
Modified Figures
and Stats

\newcommand{\anti}{{$\mathcal{A}_0$\xspace}}
\newcommand{\antf}{{$\mathcal{A}_1$\xspace}}
\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$\xspace}}

@@

We recorded the fixations on one of these 10 zones and normalized by different total video duration and surface of AOIs between the robot and human conditions. We finally analyzed their distribution, producing what we
call \emph{gaze patterns}. The difference in the gaze patterns over ``N'' AOis can be calculated as follows:\\

$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$

>>>>

\newcommand{\anti}{{$\mathcal{A}_0$ }}
\newcommand{\antf}{{$\mathcal{A}_1$ }}
\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}

@@

We collected the gazes falling into one of these 10 zones and normalized them to
account for different total video duration and surface of AOIs between the robot
and human conditions. We finally analyzed their distribution, producing what we
call \emph{gaze patterns}.
